Package Tests

### 2020-08-15 r-package/tests_marcus/rjava_tests.Rmd
Java is quite picky regarding data types, while R is more permissive. Every parameter passed that Java expects to be an integer value shall be forcefully cast to integer using as.integer() before passing to rJava. I have updated the detailed_itineraries() function to do that.

>>>>

## Rafa Tests

```{r}
library(r5r)
 library(data.table)
 library(dplyr)
 library(sf)

 # build transport network
 path <- system.file("extdata", package = "r5r")
 r5_core <- setup_r5(data_path = path)

 # load origin/destination points
 points <- read.csv(system.file("extdata/poa_hexgrid.csv", package = "r5r"))

 # input
 fromLat <- points[1,]$lat
 fromLon <- points[1,]$lon
 toLat <- points[100,]$lat
 toLon <- points[100,]$lon
 trip_date <- "2019-03-17"
 departure_time <- "14:00:00"
 street_time = 15L
 direct_modes <- c("WALK", "BICYCLE", "CAR")
 transit_modes <-"BUS"
 max_street_time = 30

 trip <- detailed_itineraries( r5_core,
                              fromLat = fromLat,
                              fromLon = fromLon,
                              toLat = toLat,
                              toLon = toLon,
                              trip_date = trip_date,
                              departure_time = departure_time,
                              direct_modes = direct_modes,
                              transit_modes = transit_modes,
                              max_street_time = max_street_time
                             )
```

```{r}
trip
```
